---
title: "Course schedule"
output:
  html_document:
    theme: cosmo

---

```{r, include = FALSE}
library(rio)
library(here)
library(kableExtra)
library(tidyverse)

data <- import(here("syllabus.csv"))

data[4,3] <- "Theories of moral development: Kohlberg's stage theory, social domain theory"
data[1,4] <- "[Syllabus](syllabus.docx)"
data[2,4] <- "[Wade (2007)](readings/week_1/Wade_2007.pdf); [Allchin (2009)](readings/week_1/Allchin_2009.pdf)"
data[3,4] <- "[Hamlin, Wynn, & Bloom (2007)](readings/week_2/Hamlin_2007.pdf); [Bloom (2010)](readings/week_2/Bloom_2010.pdf)"
data[4,4] <- "[Kohlberg (1968)](readings/week_2/Kohlberg_1968.pdf); [Smetana (2013)](readings/week_2/Smetana_2014.pdf)"
data[5,4] <- "[Greene et al. (2009)](readings/week_3/Greene_2009.pdf); [Aktas, Yilmaz, & Bahcekapili (2017)](readings/week_3/Aktas_2017.pdf)"
data[6,4] <- "[Haidt (2001)](readings/week_3/Haidt_2001.pdf); [Sauer (2012)](readings/week_3/Sauer_2012.pdf)"
data[7,4] <- "[Klein & O'Brien (2016)](readings/week_4/Klein_2016.pdf)"
data[8,4] <- "[Haidt, Koller, & Dias (1993)](readings/week_4/Haidt_1993.pdf); [Uhlmann et al. (2015)](readings/week_4/Uhlmann_2015.pdf)"
data[9,4] <- "[Butler, Burbank, & Chisholm (2011)](readings/week_5/Butler_2011.pdf); [Fehr & Gachter (2002)](readings/week_5/Fehr_2002.pdf)"
data[10,4] <- "[Sonnentag & McDaniel (2013)](readings/week_5/Sonnetag_2013.pdf); [Monin & Miller (2001)](readings/week_5/Monin_2001.pdf)"
data[12,4] <- "[Conway & Peetz (2012)](readings/week_6/Conway_2012.pdf); [Valdesolo & DeSteno (2008)](readings/week_6/Valdesolo_2008.pdf)"
data[13,4] <- "[Schnall et al. (2008)](readings/week_7/Schnall_2008.pdf); [Cronin, Reysen, & Branscombe (2012)](readings/week_7/Cronin_2012.pdf)"
data[14,4] <- "[Bastian, Jetten, & Fasoli (2011)](readings/week_7/Bastian_2011.pdf); [Bloom (2013)](readings/week_7/Bloom_2013.pdf)"
data[15,4] <- "[Stets & Carter (2011)](readings/week_8/Stets_2011.pdf)"
data[16,4] <- "[Bandura et al. (1996)](readings/week_8/Bandura_1996.pdf); [Mazar, Amir, & Ariely (2008)](readings/week_8/Mazar_2005.pdf)"
data[17,4] <- "[Graham, Haidt, & Nosek (2009)](readings/week_9/Graham_2009.pdf); [Pizarro (2012)](https://www.ted.com/talks/david_pizarro_the_strange_politics_of_disgust?language=en)"
data[18,4] <- "[Day et al. (2014)](readings/week_9/Day_2014.pdf); [Feinberg & Willer (2015)](readings/week_9/Feinberg_2015.pdf)"
data[19,4] <- "[Shariff & Norenzayan (2007)](readings/week_10/Shariff_2007.pdf); [Graham & Haidt (2010)](readings/week_10/Graham_2010.pdf)"
data[20,4] <- "[Miller, Bersoff, & Harwood (1990)](readings/week_10/Miller_1990.pdf); [An & Trafimow (2014)](readings/week_10/An_2014.pdf)"

```



Readings should be completed before the class date indicated on the schedule. 


```{r, echo = FALSE}

data %>% 
  kbl() %>% 
  kable_styling(c("striped"))
```




# Readings

- Aktaş, B., Yilmaz, O., & Bahçekapili, H. G. (2017). **Moral pluralism on the trolley tracks: Different normative principles are used for different reasons in justifying moral judgments.** *Judgment and Decision Making.*

- Allchin, D. (2009). The evolution of morality. *Evolution: Education and Outreach, 2*(4), 590-601.

- An, S., & Trafimow, D. (2014). Affect and morality: a cross-cultural examination of moral attribution. *Journal of Cross-Cultural Psychology, 45*(3), 417-430.

- Bandura, A., Barbaranelli, C., Caprara, G. V., & Pastorelli, C. (1996). Mechanisms of moral disengagement in the exercise of moral agency. *Journal of personality and social psychology, 71*(2), 364.

- Bastian, B., Jetten, J., & Fasoli, F. (2011). Cleansing the soul by hurting the flesh: The guilt-reducing effect of pain. *Psychological science, 22*(3), 334.

- Bloom, P. (2010). The moral life of babies. *New York Times Magazine*.

- Bloom, P. (2013). The baby in the well: the case against empathy. *New Yorker.*

- Butler, D. J., Burbank, V. K., & Chisholm, J. S. (2011). The frames behind the games: Player's perceptions of prisoners dilemma, chicken, dictator, and ultimatum games. *The Journal of Socio-Economics, 40*(2), 103-114.

- Conway, P., & Peetz, J. (2012). When does feeling moral actually make you a better person? Conceptual abstraction moderates whether past moral deeds motivate consistency or compensatory behavior. *Personality and Social Psychology Bulletin, 38*(7), 907-919.

- Cronin, T., Reysen, S., & Branscombe, N. R. (2012). Wal-Mart's conscientious objectors: Perceived illegitimacy, moral anger, and retaliatory consumer behavior. *Basic and Applied Social Psychology, 34*(4), 322-335.

- Day, M. V., Fiske, S. T., Downing, E. L., & Trail, T. E. (2014). Shifting liberal and conservative attitudes using moral foundations theory. *Personality and Social Psychology Bulletin, 40*(12), 1559-1573.

- Fehr, E., & Gächter, S. (2002). Altruistic punishment in humans. *Nature, 415*(6868), 137-140.

- Feinberg, M., & Willer, R. (2015). From gulf to bridge: When do moral arguments facilitate political influence? *Personality and Social Psychology Bulletin, 41*(12), 1665-1681.

- Graham, J., Haidt, J., & Nosek, B. A. (2009). Liberals and conservatives rely on different sets of moral foundations. *Journal of personality and social psychology, 96*(5), 1029.

- Graham, J., & Haidt, J. (2010). Beyond beliefs: Religions bind individuals into moral communities. *Personality and social psychology review, 14*(1), 140-150.

- Greene, J. D., Cushman, F. A., Stewart, L. E., Lowenberg, K., Nystrom, L. E., & Cohen, J. D. (2009). Pushing moral buttons: The interaction between personal force and intention in moral judgment. *Cognition, 111*(3), 364-371.

- Haidt, J., Koller, S. H., & Dias, M. G. (1993). Affect, culture, and morality, or is it wrong to eat your dog? *Journal of personality and social psychology, 65*(4), 613.

- Haidt, J. (2001). The emotional dog and its rational tail: a social intuitionist approach to moral judgment. *Psychological review, 108*(4), 814.

- Hamlin, J. K., Wynn, K., & Bloom, P. (2007). Social evaluation by preverbal infants. *Nature, 450*(7169), 557-559.

- Klein, N., & O'Brien, E. (2016). The tipping point of moral change: When do good and bad acts make good and bad actors? *Social cognition, 34*(2), 149-166.

- Kohlberg, L. (1968). The child as a moral philosopher. *Psychology today*, 25-30. 

- Miller, J. G., Bersoff, D. M., & Harwood, R. L. (1990). Perceptions of social responsibilities in India and in the United States: Moral imperatives or personal decisions? *Journal of personality and social psychology, 58*(1), 33.

- Monin, B., & Miller, D. T. (2001). Moral credentials and the expression of prejudice. *Journal of personality and social psychology, 81*(1), 33.

- Mazar, N., Amir, O., & Ariely, D. (2008). The dishonesty of honest people: A theory of self-concept maintenance. *Journal of marketing research, 45*(6), 633-644.

- Pizarro, D. (2012, May ). The strange politics of disgust [Video]. TED. https://www.ted.com/talks/david_pizarro_the_strange_politics_of_disgust?language=en

- Reeder, G. D., & Spores, J. M. (1983). The attribution of morality. *Journal of Personality and Social psychology, 44*(4), 736.

- Sonnentag, T. L., & McDaniel, B. L. (2013). Doing the right thing in the face of social pressure: Moral rebels and their role models have heightened levels of moral trait integration. *Self and Identity, 12*(4), 432-446.

- Sauer, H. (2012). Psychopaths and filthy desks. *Ethical Theory and Moral Practice, 15*(1), 95-115.

- Schnall, S., Haidt, J., Clore, G. L., & Jordan, A. H. (2008). Disgust as embodied moral judgment. *Personality and social psychology bulletin, 34*(8), 1096-1109.

- Shariff, A. F., & Norenzayan, A. (2007). God is watching you: Priming God concepts increases prosocial behavior in an anonymous economic game. *Psychological science, 18*(9), 803-809.

- Smetana, J. G. (2013). 29 Moral Development: The Social Domain Theory View.

- Stets, J. E., & Carter, M. J. (2011). The moral self: Applying identity theory. *Social Psychology Quarterly, 74*(2), 192-215.

- Uhlmann, E. L., Pizarro, D. A., & Diermeier, D. (2015). A person-centered approach to moral judgment. *Perspectives on Psychological Science, 10*(1), 72-81.

- Valdesolo, P., & DeSteno, D. (2008). The duality of virtue: Deconstructing the moral hypocrite. *Journal of Experimental Social Psychology, 44*(5), 1334-1338.

- Wade, N. (2007). Scientist finds the beginnings of morality in primate behavior. *New York Times.*
